---
title: "Week 10 Assignment"
author: "Paul Panek"
date: "July 18, 2017"
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
setwd("C:\\Users\\X\\Documents\\SMU\\DoingDataScience\\Week10\\PPanek_Week10_Assignment")
library(ggplot2) 
library(plyr) 
```
## Item 1: getting the data and saving as data1
```{r}
fileLocation <- "http://stat.columbia.edu/~rachel/datasets/nyt1.csv"
data1 <- read.csv(url(fileLocation))
head(data1)
str(data1)
```
## Item 2: Create a new variable ageGroup that categorizes age into following groups: 
###< 18, 18–24, 25–34, 35–44, 45–54, 55–64 and 65+.
```{r}
data1$ageGroup[data1$Age<18]<-"<18"
data1$ageGroup[data1$Age>=18 & data1$Age <25] <- "18–24"
data1$ageGroup[data1$Age>=25 & data1$Age <35] <- "25–34"
data1$ageGroup[data1$Age>=35 & data1$Age <45] <- "35–44"
data1$ageGroup[data1$Age>=45 & data1$Age <55] <- "45-54"
data1$ageGroup[data1$Age>=55 & data1$Age <65] <- "55-64"
data1$ageGroup[data1$Age>=65] <- "65+"
head(data1)
```
## Item 3:	Use sub set of data called “ImpSub” where Impressions > 0 ) in your data set
```{r}
ImpSub<-data1[data1$Impressions>0,]
dim(ImpSub)
```
## Item 4:  Create a new variable called click-through-rate (CTR = click/impression)
### Intentionally doing this only for ImpSub
```{r}
ImpSub$CTR <- ImpSub$Clicks/ImpSub$Impressions
dim(ImpSub)
head(ImpSub)
```
##  Item 5:  Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups.
### Using ImpSub
```{r}
Impressions <- ggplot(ImpSub, aes(x=Impressions, fill=ageGroup))+
  labs(title="Histogram of Impressions by Age Group",subtitle= "(05/01/2012)")+
  geom_histogram(binwidth=1)
Impressions

Clickthrough <- ggplot(ImpSub, aes(x=CTR, fill=ageGroup))+
  labs(title="Histogram of Click-Through Rate by Age Group",subtitle= "(05/01/2012)")+
  geom_histogram(binwidth=.025)
Clickthrough

ClickthroughGT0 <- ggplot(subset(ImpSub, CTR>0), aes(x=CTR, fill=ageGroup))+
  labs(title="Histogram of Click-Through Rate by Age Group Where Click-Through Rate >0",subtitle= "(05/01/2012)")+
  geom_histogram(binwidth=.025)
ClickthroughGT0
```

## Item 6: Define a new variable to segment users based on click -through-rate (CTR) behavior.
###  CTR< 0.2, 0.2<=CTR <0.4, 0.4<= CTR<0.6, 0.6<=CTR<0.8, CTR>0.8
```{r}
ImpSub$CTR_Group[ImpSub$CTR<.2]<-"<.2"
ImpSub$CTR_Group[ImpSub$CTR>=.2 & ImpSub$CTR <.4] <- "0.2<=CTR<0.4"
ImpSub$CTR_Group[ImpSub$CTR>=.4 & ImpSub$CTR <.6] <- "0.4<=CTR<0.6"
ImpSub$CTR_Group[ImpSub$CTR>=.6 & ImpSub$CTR <.8] <- "0.6<=CTR<0.8"
ImpSub$CTR_Group[ImpSub$CTR>=.8] <- ">=.8"
head(ImpSub)
```
## Question 7 Get the total number of Male, Impressions, Clicks and Signed_In
```{r}
Males <- sum(ImpSub$Gender)
names(Males)<-"Males"
Q7 <- c(Males,sapply(ImpSub[c(3,4,5)],sum))
Q7
```
## Question 8 Get the mean of Age, Impressions, Clicks, CTR and percentage of males and signed_In
## Perform thecalculations, create a vector from the results, then assign appropriate names.
```{r}
means <- sapply(ImpSub[c("Age", "Impressions", "Clicks", "CTR")], mean)
pcts <- sapply(ImpSub[c("Gender", "Signed_In")], function(x){sum(x) / NROW(x)})
Q8<-c(means, pcts)
names(Q8)<- c("Mean_Age","Mean_Impressions","Mean_Clicks", "Mean_CTR", "Pct_Male", "PCT_Signed_In")
Q8
```
## Item 9  Get the means of Impressions, Clicks, CTR and percentage of males and signed_In  by AgeGroup.
```{r}
ImpSub$ageGroup<-as.factor(ImpSub$ageGroup)
Mean_Age<-tapply(ImpSub$Age,ImpSub$ageGroup,mean)
Mean_Impress<-tapply(ImpSub$Impressions,ImpSub$ageGroup,mean)
Mean_Clicks<-tapply(ImpSub$Clicks,ImpSub$ageGroup,mean)
Mean_CTR<-tapply(ImpSub$CTR,ImpSub$ageGroup,mean)
Pct_Male<-tapply(ImpSub$Gender,ImpSub$ageGroup,function(x){sum(x) / NROW(x)})
Pct_Signed_in<-tapply(ImpSub$Signed_In,ImpSub$ageGroup,function(x){sum(x) / NROW(x)})

Q9<-data.frame(Mean_Age, Mean_Impress, Mean_Clicks, Mean_CTR, Pct_Male,Pct_Signed_in)
names(Q9)<-c("Mean_Age","Mean_Impress","Mean_Clicks","Mean_CTR","Pct_Male","Pct_Signed_In")
Q9

# Sanity-checking the counts and sums for Signed_In since all but first group were at 100%.
tapply(ImpSub$Signed_In,ImpSub$ageGroup,sum)
tapply(ImpSub$Signed_In,ImpSub$ageGroup,NROW)
sum(tapply(ImpSub$Signed_In,ImpSub$ageGroup,NROW))
dim(ImpSub)
```
## Item 10:  Create a table of CTRGroup vs AgeGroup counts.
```{r}
Display_Order<-c("<.2","0.2<=CTR<0.4","0.4<=CTR<0.6","0.6<=CTR<0.8",">=.8")
ImpSub$CTR_Group<-factor(ImpSub$CTR_Group, levels = Display_Order)
Q10<-with(ImpSub, tapply(Age, list(ageGroup,CTR_Group), NROW)) # Using age to count, choice of variable is meaningless because there are no NAs
Q10
```
## Item 11: Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups
### Same as Item 5.

## Item 12:  One more plot you think which is important to look at.
```{r}
ggplot(ImpSub,aes(x=Impressions, y=Clicks,fill=CTR_Group))+geom_bar(stat="identity")+labs(x="Impressions", y="Clicks",title = "Clicks by Number of Impressions and Click-Through Rate",subtitle= "(05/01/2012)",fill="Click-Through Rate")
# Total Number of Clicks centered around those with 5 to 6 impressions. Clickthough Rates drop after five impressions, although our bin size could be affecting the visibility of the dynamic.
```
